An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-28 paper/paper.tex
Paper: emphasize churn result, add mihaly as co-advisor

% TODO make title page look nicer
\begin{titlepage}
\begin{center}
\thispagestyle{empty}
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[1.75cm]
\LARGE{\textsc {\textbf{Improving the Speed of Peer to Peer Backup Systems with BitTorrent}}}\\[0.5cm]
\vspace{0.25cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.75cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{0.75cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1.5cm}
\large{\textbf{\\May 1, 2014}}\\
\end{center}
\end{titlepage}

@@

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
% TODO adjectives
% TODO format this section better
Mih\'aly H\'eder, our on-site Project Advisor, for his advice, insight, expertise, and bottomless teapot.\\

\noindent G\'abor S\'ark\"ozy, our off-site Project Advisor, for his guidance, encouragement, and editorial skills. \\

@@

After running our tests, we found that BitTorrent performs well as the data layer transport protocol for a P2P backup system. Specifically, we found that \emph{larger but fewer files are handled more efficiently than a greater number of smaller files}, given the same amount of total data. We also determined that our system handles node churn well, when the rate of churn is modeled off of the average Internet user. Our final and most important result is that \emph{our system was able to achieve data backup and recovery rates up to \~300\% quicker than the rates that could be realistically achieved in traditional backup systems.}
% TODO emphasize that our system handles node churn well, but need to reword/give numeric data

>>>>

% TODO make title page look nicer
\begin{titlepage}
\begin{center}
\thispagestyle{empty}
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[1.75cm]
\LARGE{\textsc {\textbf{Improving the Speed of Peer to Peer Backup Systems with BitTorrent}}}\\[0.5cm]
\vspace{0.25cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.75cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{1cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\vspace{.25cm}
\large{\textbf{Mih\'aly H\'eder}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1cm}
\large{\textbf{\\May 1, 2014}}\\
\end{center}
\end{titlepage}

@@

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
% TODO adjectives
% TODO format this section better
Mih\'aly H\'eder, our SZTAKI Project Advisor, for his advice, insight, expertise, and bottomless teapot.\\

\noindent G\'abor S\'ark\"ozy, our WPI Project Advisor, for his guidance, encouragement, and editorial skills. \\

@@

After running our tests, we found that BitTorrent performs well as the data layer transport protocol for a P2P backup system. Specifically, we found that \emph{larger but fewer files are handled more efficiently than a greater number of smaller files}, given the same amount of total data. We also determined that our system handles node churn well: given a rate of churn modeled off of the average Internet user, \emph{peers can expect to replace a replica every 11 days on average}. Our final and most important result is that \emph{our system was able to achieve data backup and recovery rates up to \~300\% quicker than the rates that could be realistically achieved in traditional backup systems.}
